To Be Decided

### 2025-07-19 paper/main.tex
Finish section IV-A-3

\documentclass{IEEEtran}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{subfigure}
\usepackage{xcolor}

@@

                \begin{figure*}[!htb]
                    \centering
                    \subfigure[OSM, $\chi=0.25$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_0.eps}}
                    \subfigure[OSM, $\chi=0.5$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_1.eps}}
                    \subfigure[OSM, $\chi=0.75$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_2.eps}}
                    \subfigure[OSM, $\chi=1$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_3.eps}}
                    \subfigure[OSM, $\chi=1.5$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_4.eps}} \\
                    \subfigure[SOM, $\chi=0.25$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_0.eps}}
                    \subfigure[SOM, $\chi=0.5$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_1.eps}}
                    \subfigure[SOM, $\chi=0.75$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_2.eps}}
                    \subfigure[SOM, $\chi=1$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_3.eps}}
                    \subfigure[SOM, $\chi=1.5$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_4.eps}}
                    \caption{Shape recovering study, varying contrast: reconstructed images by OSM and SOM for different contrast values.}
                    \label{fig:shape:vary:recons}
                \end{figure*}

@@

                \begin{figure}[!htb]
                    \centering
                    \subfigure[]{\includegraphics[width=0.48\columnwidth]{../experiments/vary/figs/zeta_s.eps}\label{fig:shape:vary:indicators:zeta_s}} \hspace{0.01\columnwidth}
                    \subfigure[]{\includegraphics[width=0.48\columnwidth]{../experiments/vary/figs/dnl.eps}\label{fig:shape:vary:dnl}}
                    \caption{Shape recovering study, varying contrast: (a) shape error indicator $\zeta_S$ for OSM and SOM; (b) Degree of Nonlinearity (DNL) for each contrast value.}
                    \label{fig:shape:vary:indicators}
                \end{figure}

@@

                \begin{figure}[!htb]
                    \centering
                    \subfigure[]{\includegraphics[width=.5\columnwidth]{../experiments/average/figs/dnl.pdf}\label{fig:shape:average:dnl}} \\
                    \subfigure[]{\includegraphics[width=\columnwidth]{../experiments/average/figs/plot.pdf}\label{fig:shape:average:zeta_s}}
                    \caption{Shape recovering study, average performance: (a) Degree of Nonlinearity (DNL) for each scatterer; (b) shape error indicator $\zeta_S$ for each algorithm in each instance.}
                    \label{fig:shape:average}   
                \end{figure}

@@

                Fig. \ref{fig:shape:average:zeta_s} presents the shape error indicator $\zeta_S$ for each algorithm across all test instances. The results reveal a clear performance distinction when considering LSM, which demonstrates significantly worse performance compared to the other methods. Among the remaining algorithms, while overall performance levels appear similar, some patterns emerge: OSM exhibits higher error rates across a significant number of instances, whereas CSI demonstrates superior performance in a significant portion of the test cases.

@@

                While Fig. \ref{fig:shape:average:zeta_s} provides initial insights into the results, statistical testing is important to validate the conclusions rigorously. To this end, the Friedman test \cite{friedman1937use} was applied to assess whether significant differences exist among the algorithms. The Friedman test is a non-parametric statistical test that evaluates significant differences between three or more related groups when the data does not meet the assumptions for parametric tests. In this context, the groups correspond to the algorithms, and the measurements are the $\zeta_S$ indicator values for each algorithm across all instances. Given that LSM demonstrated substantially inferior performance compared to the other algorithms, it was excluded from the statistical analysis to focus on the more competitive methods.

@@

                The Friedman test result was $p < 10^{-10}$, indicating that at least one pair of algorithms shows a significant mean paired difference. Subsequently, the Wilcoxon test was applied to identify which algorithms have significant mean paired differences between them. The p-values obtained from these tests are presented in Table \ref{tab:shape:average:pvalue}. As shown in the table, the null hypothesis that algorithms have equal performance is rejected for all algorithm pairs.

                \begin{table*}
                    \centering
                    \renewcommand{\arraystretch}{1.5}
                    \caption{Comparison of $p$-values between methods.}
                    \label{tab:shape:average:pvalue}
                    \begin{tabular}{ccccccc}
                        Pairs & OSM-BIM & OSM-CSI & OSM-SOM & BIM-CSI & BIM-SOM & CSI-SOM \\\hline
                        $p$-value & $<10{-4}$ & $<10{-8}$ & $<10{-3}$ & $<10{-2}$ & $<10{-2}$ & $<10{-8}$ \\  
                    \end{tabular}
                \end{table*}

@@

                To complement the analysis, Fig. \ref{fig:shape:average:confidence_intervals} presents the 95\% confidence intervals for the mean paired differences of the shape error indicator $\zeta_S$ for each algorithm pair. As observed, the differences consistently favor CSI, providing evidence for CSI's superiority over the other algorithms. Additionally, OSM performs significantly worse than both BIM and SOM, while BIM outperforms SOM. However, these differences average less than 5\%.

                It is worth observing that while CSI performed worse than BIM and SOM in the single scatterer study (Section \ref{sec:results:shape:star}), CSI demonstrated superior performance to both methods in this benchmarking study. This highlights the importance of conducting comprehensive benchmarking studies combined with statistical analysis to obtain more robust conclusions about algorithm average performance.

                \begin{figure}
                    \centering
                    \includegraphics[width=.8\columnwidth]{../experiments/average/figs/confidence_intervals.pdf}
                    \caption{Shape recovering study, average performance: Confidence intervals (95\%) for the shape error indicator $\zeta_S$ for each pair of algorithms.}
                    \label{fig:shape:average:confidence_intervals}
                \end{figure}

>>>>

\documentclass{IEEEtran}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{subfigure}
\usepackage{xcolor}
\usepackage{epstopdf}

\graphicspath{{../}}
\epstopdfsetup{
    program@epstopdf=epstopdf
}

@@

                \begin{figure*}[!htb]
                    \centering
                    \subfigure[OSM, $\chi=0.25$]{\includegraphics[height=1.2in]{./experiments/vary/figs/osm_0.eps}}
                    \subfigure[OSM, $\chi=0.5$]{\includegraphics[height=1.2in]{./experiments/vary/figs/osm_1.eps}}
                    \subfigure[OSM, $\chi=0.75$]{\includegraphics[height=1.2in]{./experiments/vary/figs/osm_2.eps}}
                    \subfigure[OSM, $\chi=1$]{\includegraphics[height=1.2in]{./experiments/vary/figs/osm_3.eps}}
                    \subfigure[OSM, $\chi=1.5$]{\includegraphics[height=1.2in]{./experiments/vary/figs/osm_4.eps}} \\
                    \subfigure[SOM, $\chi=0.25$]{\includegraphics[height=1.in]{./experiments/vary/figs/som_0.eps}}
                    \subfigure[SOM, $\chi=0.5$]{\includegraphics[height=1.in]{./experiments/vary/figs/som_1.eps}}
                    \subfigure[SOM, $\chi=0.75$]{\includegraphics[height=1.in]{./experiments/vary/figs/som_2.eps}}
                    \subfigure[SOM, $\chi=1$]{\includegraphics[height=1.in]{./experiments/vary/figs/som_3.eps}}
                    \subfigure[SOM, $\chi=1.5$]{\includegraphics[height=1.in]{./experiments/vary/figs/som_4.eps}}
                    \caption{Shape recovering study, varying contrast: reconstructed images by OSM and SOM for different contrast values.}
                    \label{fig:shape:vary:recons}
                \end{figure*}

@@

                \begin{figure}[!htb]
                    \centering
                    \subfigure[]{\includegraphics[width=0.48\columnwidth]{./experiments/vary/figs/zeta_s.eps}\label{fig:shape:vary:indicators:zeta_s}} \hspace{0.01\columnwidth}
                    \subfigure[]{\includegraphics[width=0.48\columnwidth]{./experiments/vary/figs/dnl.eps}\label{fig:shape:vary:dnl}}
                    \caption{Shape recovering study, varying contrast: (a) shape error indicator $\zeta_S$ for OSM and SOM; (b) Degree of Nonlinearity (DNL) for each contrast value.}
                    \label{fig:shape:vary:indicators}
                \end{figure}

@@

                \begin{figure}[!htb]
                    \centering
                    \subfigure[]{\includegraphics[width=.5\columnwidth]{./experiments/average/figs/dnl.eps}\label{fig:shape:average:dnl}} \\
                    \subfigure[]{\includegraphics[width=\columnwidth]{./experiments/average/figs/plot.eps}\label{fig:shape:average:zeta_s}}
                    \caption{Shape recovering study, average performance: (a) Degree of Nonlinearity (DNL) for each scatterer; (b) shape error indicator $\zeta_S$ for each algorithm in each instance.}
                    \label{fig:shape:average}   
                \end{figure}

@@

                Fig. \ref{fig:shape:average:zeta_s} presents the shape error indicator $\zeta_S$ for each algorithm across all test instances. The results reveal a clear performance distinction when considering LSM, which demonstrates significantly worse performance compared to the other methods. Among the remaining algorithms, while overall performance levels appear similar, some patterns emerge: CSI exhibits higher error rates across a significant number of instances, whereas BIM demonstrates superior performance in a significant portion of the test cases.

@@

                While Fig. \ref{fig:shape:average:zeta_s} provides initial insights into the results, statistical testing is important to validate the conclusions rigorously. To this end, Randomized Complete Block Design (RCBD) was applied to assess whether significant paired differences exist among the algorithms. RCBD is a statistical test which is used to evaluate significant paired differences between three or more related groups when the data meet the assumptions for parametric tests. In this context, the groups correspond to the algorithms, and the measurements are the $\zeta_S$ indicator values for each algorithm across all instances. Given that LSM demonstrated substantially inferior performance compared to the other algorithms, it was excluded from the statistical analysis to focus on the more competitive methods.

@@

                After validating normality assumption, the p-value computed by RCBD result was less than $10^{-15}$, indicating that at least one pair of algorithms shows a significant mean paired difference. Subsequently, multiple paired T-Test with Bonferroni correction were applied to identify which algorithms have significant mean paired differences between them. The p-values obtained from these tests are presented in Table \ref{tab:shape:average:pvalue}. As shown in the table, the null hypothesis that algorithms have equal performance is rejected for all algorithm pairs, except for OSM-SOM, indicating that OSM and SOM do not exhibit a significant difference in their average performance.

                \begin{table*}
                    \centering
                    \renewcommand{\arraystretch}{1.5}
                    \caption{Shape recovering study, average performance: $p$-values for the paired T-Test with Bonferroni correction.}
                    \label{tab:shape:average:pvalue}
                    \begin{tabular}{ccccccc}
                        Pairs & OSM-BIM & OSM-CSI & OSM-SOM & BIM-CSI & BIM-SOM & CSI-SOM \\\hline
                        $p$-value & $<10^{-2}$ & $<10^{-11}$ & 0.15 & $<10^{-7}$ & $<10^{-4}$ & $<10^{-6}$ \\  
                    \end{tabular}
                \end{table*}

@@

                To complement the analysis, Fig. \ref{fig:shape:average:confidence_intervals} presents the 95\% confidence intervals for the mean paired differences of the shape error indicator $\zeta_S$ for each algorithm pair. As observed, the differences consistently favor BIM, providing evidence for BIM's superiority over the other algorithms. Additionally, CSI performs significantly worse than both BIM, OSM and SOM. However, all differences in average performance are less than 7\%.

                Furthermore, it is noteworthy that BIM also achieved the best performance in the study from Section \ref{sec:results:shape:star}. However, while the difference between SOM and OSM was significant in the experiment from Section \ref{sec:results:shape:star}, this benchmarking study provided evidence for performance equivalence between these two methods. In other words, if conclusions were drawn based solely on the case study, this could lead to a misconception about the performance of these two methods in this problem configuration. Therefore, this reinforces the importance of conducting benchmarking studies combined with statistical analyses to obtain more robust conclusions about algorithm performance.

                \begin{figure}
                    \centering
                    \includegraphics[width=.8\columnwidth]{./experiments/average/figs/confidence_intervals.eps}
                    \caption{Shape recovering study, average performance: Confidence intervals (95\%) for the shape error indicator $\zeta_S$ for each pair of algorithms.}
                    \label{fig:shape:average:confidence_intervals}
                \end{figure}
